Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-06-24 snapshot_system/intro.tex
adding exper.
modify all sections

\begin{figure}[htb]
    \centering
    \includegraphics[width=3in]{images/traditional-arch.pdf}
    \label{fig-traditional-arch}
    \caption{Traditional VM Backup System}
\end{figure}

This paper seeks for a low-cost architecture option and takes advantage of the
fact that the
backup service collocates on the cloud cluster with a minimum resource usage
(Figure~\ref{fig-colocated-arch})
%Since most of backup data is not used in practice, system resource in such a service is not fully utilized.
%The dirty bit approach~\cite{??}  which checks the version difference can effectively remove
%duplicates while using content fingerprints can significantly compress more~\cite{Bottlneck08}.
%On the other hand, comparing fingerprints  adds significant  memory cost. 
%Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently.
Cloud providers often wish that the backup service only consumes  small or modest resources
with a minimal impact to the existing cloud services.  
We study and evaluate the integration of several deduplication strategies to meet
the low-cost collocation requirement. In parallel, we identify deduplication options that yield
better fault isolation.
%A recent study using subsampling~\cite{Guo2011}  can significantly reduce the memory requirement.
We achieve improved fault isolation by accounting for the fact that after
deduplication most data blocks are shared by several to many virtual machines.
Failure of such popluar blocks would have a catastrophic effect and many
snapshots of virtual machines would be affected.
The previous work in deduplication focuses mainly on the efficiency and approximation of
finger print comparison, and has not addressed fault tolerance along with a low-cost solution.
Another issue considered is that
%that deletion of old snapshots compete for computing resource as well. That is because data dependence created
deletion of old snapshots compete for computing resources as well so deletion needs
to be considered in system design. The additional complexity for deletions
come from the dependencies created by multiple links to the same problem, so
some solution is needed to determine blocks with no dependent snapshots after deletion.
% especially when  VMs can migrate around in the cloud.

\begin{figure}[htb]
    \centering
    \includegraphics[width=3in]{images/colocated-arch.pdf}
    \label{fig-colocated-arch}
    \caption{Colocated VM Backup System}
\end{figure}

The paper studies and evaluates  an integrated approach which uses  multiple duplicate detection strategies
based on  version  detection, inner VM duplicate search,
and controlled cross-VM comparison. 
This approach is VM centric by localizing duplicate detection within each VM  as much as possible
and minimize memory usage while delivering a decent deduplication efficiency. 
Our partially localized solution also brings the benefits of parallelism, utilization, and fault isolation.
Our deletion strategy uses a double Bloom filter strategy for periodic mark-and-sweeping of expired data blocks.
We have developed a prototype system that runs a cluster of Linux machines with Xen.
The backup storage uses a standard distributed file system with data replication and block packaging,
and we allocate more  replicas for the commonly-shared  data blocks among VM snapshots to enhance fault tolerance.

%************** Paper sections summary
%THIS NEEDS MODIFICATION
The rest of this paper is organized as follows.
Section~\ref{review} reviews background and related work.
Section~\ref{sec:framework}  discusses the  design framework and system architecture.
Section~\ref{sec:model}  analyzes the benefit of our approach for fault isolation. 
Section~\ref{exper} is our experimental evaluation that compare with the other approach.
Section~\ref{conc}  concludes this paper.

>>>>

%\begin{figure}[htb]
%    \centering
%    \includegraphics[width=3in]{images/traditional-arch.pdf}
%    \label{fig-traditional-arch}
%    \caption{Traditional VM Backup System}
%\end{figure}

This paper seeks for a low-cost architecture option and takes advantage of the
fact that the
backup service collocates on the cloud cluster with a minimum resource usage
(Figure~\ref{fig-colocated-arch})
%Since most of backup data is not used in practice, system resource in such a service is not fully utilized.
%The dirty bit approach~\cite{??}  which checks the version difference can effectively remove
%duplicates while using content fingerprints can significantly compress more~\cite{Bottlneck08}.
%On the other hand, comparing fingerprints  adds significant  memory cost. 
%Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently.
Cloud providers often wish that the backup service only consumes  small or modest resources
with a minimal impact to the existing cloud services.  
We study and evaluate the integration of several deduplication strategies to meet
the low-cost collocation requirement. In parallel, we identify deduplication options that yield
better fault isolation.
%A recent study using subsampling~\cite{Guo2011}  can significantly reduce the memory requirement.
We achieve improved fault isolation by accounting for the fact that after
deduplication most data chunks are shared by several to many virtual machines.
Failure of such popular data chunks would have a catastrophic effect and many
snapshots of virtual machines would be affected.
The previous work in deduplication focuses on the efficiency and approximation of
finger print comparison, and has not addressed fault tolerance together with deduplication.
% along with a low-cost solution.
%Another issue considered is that
%that deletion of old snapshots compete for computing resource as well. That is because data dependence created
%deletion of old snapshots compete for computing resources as well so deletion needs
%to be considered in system design. The additional complexity for deletions
%come from the dependencies created by multiple links to the same problem, so
%some solution is needed to determine blocks with no dependent snapshots after deletion.
% especially when  VMs can migrate around in the cloud.

%\begin{figure}[htb]
%    \centering
%    \includegraphics[width=3in]{images/colocated-arch.pdf}
%    \label{fig-colocated-arch}
%    \caption{Collocated VM Backup System}
%\end{figure}

The paper studies and evaluates  an integrated approach which uses  multiple duplicate detection strategies
based on  version  detection, inner VM duplicate search,
and controlled cross-VM comparison. 
This approach is VM centric by localizing duplicate detection within each VM  
and by packaging data chunks from the same VM into a file system block as much as possible.
The solution uses  a small amount of  memory while delivering a decent deduplication efficiency. 
Our localization solution also brings the benefits of parallelism, resource utilization, and fault isolation.
Our deletion strategy uses a double Bloom filter strategy for periodic mark-and-sweeping of expired data.
We have developed a prototype system that runs a cluster of Linux machines with Xen.
The backup storage uses a standard distributed file system with data replication and block packaging,
and we allocate more  replicas for the commonly-shared  data blocks among VM snapshots to enhance fault tolerance.

%************** Paper sections summary
%THIS NEEDS MODIFICATION
The rest of this paper is organized as follows.
Section~\ref{review} reviews background and related work.
Section~\ref{sec:framework}  discusses the  design options for snapshot backup with a VM-centric approach. 
Section~\ref{sec:model}  analyzes the benefit of our approach for fault isolation. 
Section~\ref{sec:arch}  describes our system architecture and implementation details.
%   the benefit of our approach for fault isolation. 
Section~\ref{exper} is our experimental evaluation that compare with the other approaches.
Section~\ref{conc}  concludes this paper.

### 2013-06-24 snapshot_system/snapshot.tex
adding exper.
modify all sections

A deduplication scheme compares the fingerprints of the current snapshot
with its parent snapshot and also other snapshots in the entire cloud.
The traditional approach compares all fingerprints and 
stores one copy for all of a block's duplicates.
We call this as  the VM-oblivious (VO) approach.
In comparison, we analyze the design of
a VM-centric approach (VC) which differenates duplicates within a VM and cross VMs,
and conducts \textit{Inner-VM} and \textit{cross-VM} detection seperately.

@@

Inner-VM duplication can be very effecive within VM's snapshots. There
are typically a large number of duplicates existing among the snapshots
for a single VM.  Localizing the snapshot data deduplication witin a VM
improves the system by:
increasing data independency between different VM backups,
simplifying snapshot management and statistics collection,
and facilitating parallel execution of snapshot operations.
On the other hand, cross-VM duplication can also be desirable mainly due to widely-used software and libraries. 
As the result, different VMs tend to backup large amount of highly similar data.
We integrate those strategies together as follows.
%Our multi-level pipeline process can minimize 
%the cost of deduplication while maximize the its efficiency at each level,
%and it is parallel since each segment is processed independently.

\begin{itemize}
\item \textbf{Dirtybit-based corase-grain inner-VM deduplication.}
The first-level deduplication is to follow the standand dirty bit approach, but is conducted
in the coarse grain segment level.
We use the  Xen virtual device driver which supports changed block tracking
for the storage device
and the dirty bit setting is maintained in a corase grain level we call it a segment.
In our implementation, the segment size is 2MB. 
Since every write for a block will touch a dirty bit, the device driver maintains dirtybits in memory
and cannot affort a small segment  size.

It should be noted that changed block tracking is supported or can be easily implemented in many 
major virtualization solution vendors. 
%(VMware, Xen, Microsoft).  
VMware support it directly; the VMWare hypervisor has an API to let external backup application know 
the changed areas since last backup. Xen doesn't directly support it, However, their open-source 
architecture allows anyone to extend the device driver, thus enabling changed block tracking. 
We implement dirty bit tracking this way in Alibaba's platform.  
The Microsoft SDK provides an API that allows external applications to monitor 
the VM's I/O traffic, therefore changed block tracking can be implemented externally.

\item \textbf{Chunk-level fine-grain inner-VM detection.}
The best deduplication uses a nonuniform chunk size 
in the average of 4K or 8K~\cite{??}. This allows the system to
achieve deduplication even when there are insertions/deletions which would
affect many fixed-size blocks.
Thus the second-level inner-VM deduplication is to perform this chunking for
dirty segments, and to compare the snapshot with its parent. 
We load the fingerprints of block chunks of the corresponding segment from the
parent and perform fingerprint matching for further inner-VM deduplication.
The amount of memory for maintaining those fingerprints  is small, as we only
load one segment at a time.
For example, with a 2MB segment, there are about 500 fingerprints to compare.

@@

\item \textbf{Cross-VM deduplication.}
This step accomplishes the standand global fingerprint  comparison as conducted
in the previous work~\cite{??}.
One key observation is that the inner deduplication has removed many of the duplicates.
There are fewer deduplication opportunities across VMs while the memory and network
consumption for global comparison is more expensive.
Thus our approximation is that the global fingerprint comparison only searches for the most popular items. 
%Since duplicate sharing patterns among  VM follows a zip-like distribution,  
\end{itemize}

When a block is not detected as a duplicate to any existing block, this block will be written
to the file system. Since the backend file system typically uses a large block size such as 64MB, each VM will 
accululate small local blocks. We manage this accumulation process using an apendstore  scheme
and discuss this in details in Section~\ref{sect:arch}.

 \subsection{Popular Chunk Management}
%VM-oriented Fault Isolation}
%Our objective for fault isolation is to minimize the number of VMs affected when there are failures
%in the cluster.  
%The inner-VM deduplication does not depend on any global service and the comparison
%for each VM is localized within the parent and the current snapshot.
%Lack of data dependence between VMs brings 
With cross-VM deduplication, shared data blocks
create an artifical dependence  among VMs and failure of one shared block
affects many VMs. Thus we only maintain the index for a small set of popular chunks.
The management for popular data chunks contains two aspects.
\begin{itemize}
\item Compute and select top-$k$ most popular chunks.
The popularity of a chunk is the number  of data blocks from different VMs
that are duplicates of this block after the inner VM deduplication.
This number can be computed perioidically in a weekly basis.
Once the popularity of all data blocks is collected, the system only maintains the top $k$
most popular blocks.  For cross-VM comparison,
we only store  top $k$ items and $k$ is chosen to be relatively small.
Our analysis below will show that the algorithm can still deliver competitive
deduplication effiency after making these approximations.
\item  Since $k$ is small and these top $k$ blocks are shared among multiple VMs, 
we can afford to provide extra replicas for these popular blocks to enhanace the fault resilence.
We will provide an analysis of the fault tolerance in the next subsection.
\end{itemize}

This section analyzes how value   $k$ impacts the deduplication efficiency.
%It also  compares the  fault resilience of our VM-centric deduplication approach with a standand approach using 
%global deduplication.
%\subsubsection{Impact of CDS deduplication}
The analysis is based on VM traces collected
using Alibaba's production user data~\cite{ieeecloud} 
which shows that the popularity of data blocks after inner VM deduplication follows 
a Zipf-like distribution\cite{zipf} and its
exponent $\alpha$ is ranged between 0.65  and  0.70.
%As a result, it can be proved that deduplication efficiency of CDS index is scalable:

\begin{table}[ht]
\centering
\begin{tabular}{|p{1.25cm}|p{6.5cm}|}
\hline
$b$ &  the total amount of data blocks\\ 
\hline
$b_u$ &  the total amount of unique fingerprints after inner VM  deduplication\\
\hline
$C_i$ &  the frequency for the $i$th most popular fingerprint\\
\hline
$\delta$ &  the percentage of duplicates detected in inner VM deduplication\\
\hline
$\sigma$ &  the number of uniqie non-CDS chunks over  the number of the CDS chunks.\\
\hline
$p$ & the number of machines in the cluster\\
\hline
$D$ & the amount of unique data on each machine\\
\hline
$B$ & the average data chunk size. Our setting is  4K.\\
\hline
$s$ & the average size of file system blocks in the distributed file system. The default is  64MB.\\
\hline
$m$ & memory size on each node used by VC\\ 
\hline
$F$ & the size of an polular data index entry\\
$N_1$ & the average number  of non-CDS file system blocks  in a VM\\
$N_2$ & the average number  of CDS file system blocks  in a VM\\
$N_o$ & the average number  of file system blocks  in a VM for VO\\
\hline
\end{tabular}
\caption{Modeling  symbols.}
\label{tab:symbol}
\end{table}

Let $b$ be the total number of data blocks after localized deduplication, 
$b_u$ be the total number of fingerprints 
in the global index after complete deduplication, and
$C_i$ be the frequency for the $i$th most popular fingerprint. 
By Zipf-like distribution, $C_i = \frac{C_1}{i^\alpha}.$
Since $ \sum_{i=1}^{b_u}C_i = b$,
\[
C_1 \sum_{i=1}^{b_u}\frac{1}{i^\alpha} = b
\]
Given $\alpha <1$, $C_1$ can be approximated with integration:
\begin{equation}
C_1=\frac{b(1-\alpha)}{b_u^{1-\alpha}}.
\end{equation}

@@

The  $k$ most popular fingerprints can cover the following number of blocks after inner VM 
deduplication.
\[
C_1 \sum_{i=1}^{k}\frac{1}{i^\alpha} \approx  
C_1 \int_{1}^{k}\frac{1}{x^\alpha} dx  \approx  C_1\frac{  k^{1-\alpha}} {1-\alpha}.
\]

Deduplication efficiency of VC using top $k$ popular blocks
is the percentage of duplicates that can be detected:  
\begin{equation}
\begin{split}
e_k &= 
\frac{ b(1-\delta) + C_1\frac{  k^{1-\alpha}} {1-\alpha}} 
{b(1-\delta)  + \delta b - b_u }\\
&= 
\frac{ (1-\delta) + \delta  (\frac{k}{b_u})^{1-\alpha}}
{ 1- \frac{b_u}{b} }.
\end{split}
\end{equation}

@@

%[Describe the dedup efficiency model in detail]
Let $p$ be the number of physical machines in the cluster, $m$ be the memory on each node used by the popular
index, $F$ be the size of an index entry,
$D$ be the amount of unique data on each phyiscal machine, and 
$B$ be the average block size. We store the popular index using a distribued shared memory hashtable
such as MemCacheD.  Then $k$ and $b_u$ can be expressed as:
$
k = p*m/F$, and $b_u = p*D/B.
$

The overall deduplication effiency of VC is
\[
\frac{ (1-\delta) + \delta (\frac{m*B}{D*F})^{1-\alpha}}
{ 1- \frac{b_u}{b} }.
\]
where $(\frac{m*B}{D*F})^{1-\alpha}$ represents the percentage of the remaining blocks detected as duplicates
after inner VM deduplication. 
%Then the deduplication efficiency of CDS approach using top k most popular fingerprints is:
%\begin{equation}
%  e_k = (\frac{m*B}{F*D})^{1-\alpha}
%\end{equation}

When the number of machines at each cluster increases, the number of total VMs increases.
Then $k$ increases since more memory is available to host the popular block index.
But for each physical machine, the number of VMs remains the same, and thus
$D$ is  a constant. Then  the overall deduplication efficiency of VC remains
a constant.

>>>>

A deduplication scheme compares the fingerprints of the current snapshot
with its parent snapshot and also other snapshots in the entire cloud.
The traditional approach compares all fingerprints and 
stores one copy for all of a chunk's duplicates.
We call this as  the VM-oblivious (VO) approach.
In comparison, we analyze the design of
a VM-centric approach (VC) which differentiates duplicates within a VM and cross VMs,
and conducts \textit{Inner-VM} and \textit{cross-VM} detection separately.

@@

Inner-VM duplication can be very effective within VM's snapshots. There
are typically a large number of duplicates existing among the snapshots
for a single VM.  Localizing the snapshot data deduplication within a VM
improves the system by:
increasing data independence between different VM backups,
simplifying snapshot management and statistics collection,
and facilitating parallel execution of snapshot operations.
On the other hand, cross-VM duplication can also be desirable mainly due to widely-used software and libraries. 
As the result, different VMs tend to backup large amount of highly similar data.
We integrate those strategies together as follows.
%Our multi-level pipeline process can minimize 
%the cost of deduplication while maximize the its efficiency at each level,
%and it is parallel since each segment is processed independently.

\begin{itemize}
\item \textbf{Dirtybit-based coarse-grain inner-VM deduplication.}
The first-level deduplication is to follow the standard dirty bit approach, but is conducted
in the coarse grain segment level.
We use the  Xen virtual device driver which supports a feature called "changed block tracking''
for the storage device
and the dirty bit setting is maintained in a coarse grain level we call it a segment.
In our implementation, the segment size is 2MB. 
Since every write for a segment will touch a dirty bit, the device driver maintains dirty bits in memory
and cannot afford a small segment  size.

It should be noted that dirtybit tracking is supported or can be easily implemented in many 
major virtualization solution vendors. 
%(VMware, Xen, Microsoft).  
VMware support it directly; the VMWare hypervisor has an API to let external backup application know 
the changed areas since last backup. Xen doesn't directly support it, However, their open-source 
architecture allows anyone to extend the device driver, thus enabling changed block tracking. 
We implement dirty bit tracking this way in Alibaba's platform.  
The Microsoft SDK provides an API that allows external applications to monitor 
the VM's I/O traffic, therefore changed block tracking can be implemented externally.

\item \textbf{Chunk-level fine-grain inner-VM detection.}
The best deduplication uses a nonuniform chunk size 
in the average of 4K or 8K~\cite{??}. This allows the system to
achieve deduplication even when there are insertions/deletions which would
affect many fixed-size chunks.
Thus the second-level inner-VM deduplication is to perform this chunking for
dirty segments, and to compare the snapshot with its parent. 
We load the chunk fingerprints in the corresponding segment from the
parent and perform fingerprint matching for further inner-VM deduplication.
The amount of memory for maintaining those fingerprints  is small, as we only
load one segment at a time.
For example, with a 2MB segment, there are about 500 fingerprints to compare.

@@

\item \textbf{Cross-VM deduplication.}
This step accomplishes the standard global fingerprint  comparison as conducted
in the previous work~\cite{??}.
One key observation is that the inner deduplication has removed many of the duplicates.
There are fewer deduplication opportunities across VMs while the memory and network
consumption for global comparison is more expensive.
Thus our approximation is that the global fingerprint comparison only searches for the most popular items. 
%Since duplicate sharing patterns among  VM follows a zip-like distribution,  
\end{itemize}

When a chunk is not detected as a duplicate to any existing chunk, this chunk will be written
to the file system. Since the backend file system typically uses a large block size such as 64MB, each VM will 
accumulate small local chunk. We manage this accumulation process using an append-store  scheme
and discuss this in details in Section~\ref{sect:arch}.
The system allows all machines conduct the backup in parallel in different machines, and each machine
conducts the backup of one VM at a time, and thus only requires a write  buffer for one VM.

It should be noted that CDS chunks are computed periodically and all CDS chunks are stored in a separate
append-store instance. In this way, each file block for non-CDS chunks is associated with one VM
and does not contain any CDS chunk.

 \subsection{Popular Chunk Management}
%VM-oriented Fault Isolation}
%Our objective for fault isolation is to minimize the number of VMs affected when there are failures
%in the cluster.  
%The inner-VM deduplication does not depend on any global service and the comparison
%for each VM is localized within the parent and the current snapshot.
%Lack of data dependence between VMs brings 
With cross-VM deduplication, shared data chunks
create an artificial dependence  among VMs. 
Thus we only maintain the index for the most popular chunks to reduce the inter-VM dependence
while still accomplishing competitive deduplication efficiency.

The management for popular data chunks contains two aspects.
\begin{itemize}
\item Compute and select top-$k$ most popular chunks.
The popularity of a chunk is the number  of data chunks  from different VMs
that are duplicates of this chunk after the inner VM deduplication.
This number can be computed periodically in a weekly basis.
Once the popularity of all data chunks is collected, the system only maintains the top $k$
most popular chunks.  For cross-VM comparison,
we only store  top $k$ items and $k$ is chosen to be relatively small.
Our analysis below will show that the algorithm can still deliver competitive
deduplication efficiency after making these approximations.
\item  Since $k$ is small and these top $k$ chunks are shared among multiple VMs, 
we can afford to provide extra replicas for these popular chunks to enhance the fault resilience.
We will provide an analysis of the space need and fault tolerance in the next subsection.
\end{itemize}

This section analyzes how value   $k$ impacts the deduplication efficiency.
%It also  compares the  fault resilience of our VM-centric deduplication approach with a standand approach using 
%global deduplication.
%\subsubsection{Impact of CDS deduplication}
The analysis is based on VM traces collected
using Alibaba's production user data~\cite{ieeecloud} 
which shows that the popularity of data chunks after inner VM deduplication follows 
a Zipf-like distribution\cite{zipf} and its
exponent $\alpha$ is ranged between 0.65  and  0.70.
%As a result, it can be proved that deduplication efficiency of CDS index is scalable:

\begin{figure}
\centering
%\epsfig{file=log-log.disk.pdf,width=3in}
%source ../vm_snapshot_sim/images/log-log.disk.eps
 \includegraphics[width=3in]{log-log-disk.pdf}
\caption{Duplicate frequency versus  chunk ranking in a log scale.}
\label{fig:Datazipf}
\end{figure}

\begin{table}[ht]
\centering
\begin{tabular}{|p{1.25cm}|p{6.5cm}|}
\hline
$b$ &  the total amount of data chunks\\ 
\hline
$b_u$ &  the total amount of unique fingerprints after inner VM  deduplication\\
\hline
$C_i$ &  the frequency for the $i$th most popular fingerprint\\
\hline
$\delta$ &  the percentage of duplicates detected in inner VM deduplication\\
\hline
$\sigma$ &  the number of unique non-CDS chunks over  the number of the CDS chunks.\\
\hline
$p$ & the number of machines in the cluster\\
\hline
$D$ & the amount of unique data on each machine\\
\hline
$B$ & the average data chunk size. Our setting is  4K.\\
\hline
$s$ & the average size of file system blocks in the distributed file system. The default is  64MB.\\
\hline
$m$ & memory size on each node used by VC\\ 
\hline
$F$ & the size of an popular data index entry\\
$N_1$ & the average number  of non-CDS file system blocks  in a VM\\
$N_2$ & the average number  of CDS file system blocks  in a VM\\
$N_o$ & the average number  of file system blocks  in a VM for VO\\
\hline
\end{tabular}
\caption{Modeling  symbols.}
\label{tab:symbol}
\end{table}

Let $b$ be the total number of data chunks after localized deduplication, 
$b_u$ be the total number of fingerprints 
in the global index after complete deduplication, and
$C_i$ be the frequency for the $i$th most popular fingerprint. 
By Zipf-like distribution, $C_i = \frac{C_1}{i^\alpha}.$
Since $ \sum_{i=1}^{b_u}C_i = b$,
\[
C_1 \sum_{i=1}^{b_u}\frac{1}{i^\alpha} = b
\]
Given $\alpha <1$, $C_1$ can be approximated with integration:
\begin{equation}
C_1=\frac{b(1-\alpha)}{b_u^{1-\alpha}}.
\end{equation}

@@

The  $k$ most popular fingerprints can cover the following number of chunks after inner VM 
deduplication.
\[
C_1 \sum_{i=1}^{k}\frac{1}{i^\alpha} \approx  
C_1 \int_{1}^{k}\frac{1}{x^\alpha} dx  \approx  C_1\frac{  k^{1-\alpha}} {1-\alpha}.
\]

Deduplication efficiency of VC using top $k$ popular chunks
is the percentage of duplicates that can be detected:  
\begin{equation}
\begin{split}
e_k &= 
\frac{ b(1-\delta) + C_1\frac{  k^{1-\alpha}} {1-\alpha}} 
{b(1-\delta)  + \delta b - b_u }\\
&= 
\frac{ (1-\delta) + \delta  (\frac{k}{b_u})^{1-\alpha}}
{ 1- \frac{b_u}{b} }.
\end{split}
\end{equation}

@@

%[Describe the dedup efficiency model in detail]
Let $p$ be the number of physical machines in the cluster, $m$ be the memory on each node used by the popular
index, $F$ be the size of an index entry,
$D$ be the amount of unique data on each physical machine, and 
$B$ be the average chunks size. We store the popular index using a distributed shared memory hashtable
such as MemCacheD.  Then $k$ and $b_u$ can be expressed as:
$
k = p*m/F$, and $b_u = p*D/B.
$

The overall deduplication efficiency of VC is
\[
\frac{ (1-\delta) + \delta (\frac{m*B}{D*F})^{1-\alpha}}
{ 1- \frac{b_u}{b} }.
\]
where $(\frac{m*B}{D*F})^{1-\alpha}$ represents the percentage of the remaining chunks detected as duplicates
after inner VM deduplication. 
%Then the deduplication efficiency of CDS approach using top k most popular fingerprints is:
%\begin{equation}
%  e_k = (\frac{m*B}{F*D})^{1-\alpha}
%\end{equation}

When the number of machines at each cluster increases, the number of total VMs increases.
Then $k$ increases since more memory is available to host the popular chunks index.
But for each physical machine, the number of VMs remains the same, and thus
$D$ is  a constant. Then  the overall deduplication efficiency of VC remains
a constant.
